Generalized Plackett-Luce Likelihoods

### 2024-05-08 inst/paper.tex
issue #153, bullet point 4 (shorten long section titles)

\subsection{Computational methodology for generalized Plackett-Luce likelihood functions}

@@

\section{Exact analytical solution for some simple generalized Plackett-Luce likelihood functions}

@@

\section{An alternative to the Mann-Whitney test using generalized Plackett-Luce likelihood}

@@

\subsection{A generalization of the Mann-Whitney test using
generalized Plackett-Luce likelihood}

@@

\section{Formula 1 motor racing: The Constructors' Championship}\label{f1}

>>>>

\subsection{Computational methodology}

@@

\section{Exact analytical solutions}

@@

\section{An alternative to the Mann-Whitney test}

@@

\subsection{A generalization of the Mann-Whitney test}

@@

\section{Formula 1 motor racing}\label{f1}
